Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-03 Manuscript Analyses/manuscript_analysis.Rmd
intelligibility change models

effect_plot <- function(mod, var, var2 = NULL, int = TRUE, num = 5) {
  dat = effect_data(mod)

@@

>>>>

effect_plot <- function(mod, var, var2 = NULL, int = TRUE, num = 3) {
  dat = effect_data(mod)

@@

## Models of Cognition and Intelligibility Change

mod_fun2 <- function(speaker, title) {
  subsetted = cor_df %>%
    dplyr::select(-c(fluid_cog_c, improvement)) %>%
    dplyr::mutate(pwc_diff = resid(lm(posttest ~ pretest))) %>%
    dplyr::select(pwc_diff, ends_with("_c"), speaker) %>%
    tidyr::drop_na(pwc_diff, ends_with("_c"), speaker) %>%
    dplyr::filter(speaker == {{speaker}}) %>%
    dplyr::select(-speaker) %>%
    rename(pwc = pwc_diff)

  mod.1 = training(subsetted, "glmnet", int = F)
  mod.2 = training(subsetted, "glmnet", int = T)

  return(list(mod.1, mod.2))

}

mods12 = mod_fun2("AM1")
mods22 = mod_fun2("PDM10")

p12 = plot_fun(mods12, "a) Ataxic")
p22 = plot_fun(mods22, "b) PD")

p12
```

p22

AM1_change_mod <- in_and_out(mods12, "Ataxic")

PDM10_change_mod <- in_and_out(mods22, "PD")

change_mods <- rbind(AM1_change_mod, PDM10_change_mod)

change_mods %>%
  gt::gt() %>%
  cols_label(speaker = "Speaker",
             mods = "Model Specification",
             out_sample_r2 = "R\U00B2",
             out_sample_rmse = "RMSE")

t_for_diff(mods12)
t_for_diff(mods22)

## AM1 Effect Plots

effect_plot(mods12, list_sort_c, vocab_c)
effect_plot(mods12, vocab_c, list_sort_c)
effect_plot(mods12, list_sort_c, int = F)
effect_plot(mods12, pattern_c, int = F)
effect_plot(mods12, list_sort_c, flanker_c)
effect_plot(mods12, flanker_c, list_sort_c)

## PDM10 Effect Plots

effect_plot(mods22, vocab_c, pic_seq_c)
effect_plot(mods22, pic_seq_c, vocab_c)
effect_plot(mods22, vocab_c, int = F)
effect_plot(mods22, list_sort_c, flanker_c)
effect_plot(mods22, flanker_c, list_sort_c)
